Aracna: An Open-Source Quadruped Platform for Evolutionary Robotics

### 2012-05-19 paper_aracna/main.tex
first pass through the paper done...now waiting for data and images from new robot

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{fig5.jpg}
\caption{Rendered CAD model of Aracna.}
\label{cadModelOfRobot}
\end{center}
\end{figure}

@@

Initially, we eliminated the QuadraTot's fit-PC, an onboard Linux computer weighing 370g, and replaced it with an ArbotiX microcontroller that weights only 47g. As a result, the main processing occurs on an external computer and commands are sent to Aracna wirelessly. This change, of course, comes of the cost of the robot being truly autonomous.

@@

A final change was to upgrade the power of the servo motors in order to increase the ability of the robot to strike whichever configurations are specified by the learning algorithms. Specifically, we upgraded from Dynamixel AX 12+ motors to AX-18 motors, which provide INSERT-SENTENCE-ON-DIFFERENCE-IN-SERVO-POWER.

@@

The body of Arcana takes advantage of 3D printing technology, also known as additive manufacturing, which generates physical objects from digital designs by building them up layer by layer~\citep{gibson2009additive, lipson2010factory}. The use of 3D printing means that other Aracna users can easily make copies of Aracna, either by having access to a 3D printer or via online 3D printing services such as Shapeways.com. Either option requires the 3D design files in the STereoLithography (STL) format, which we are publishing in the online support material for this paper~\citep{WEB}. Moreover, to catalyze innovation in this open-source hardware project, we are also providing the source files for the SolidWorks computer-aided-design program, because it is easier to modify a design with the original source files than with STL files. It should thus be easy for future Aracna users to improve or alter the design and quickly obtain a physical instantiation of the design. Importantly, the use of 3D printing eliminates the need to know how to machine parts, allowing many more researchers to participate in using physical robot morphologies that they design themselves. These ideas are in line with a broader trend toward enabling non-technical users to design and manufacture physical objects~\citep{clune2011objects, clune2011endless, lipson2010factory}.

@@

\section{Specifications}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.37\textwidth]{fig2.jpg}
\caption{Robot printed as one piece with support material intact.}
\label{notYetCleanedOnePieceRobot}
\end{center}
\end{figure}

@@

The four-bar
mechanisms also satisfied the design goal of making a robot that had
non-traditional movements. There is not a one-to-one mapping between the servo output and the movement of the joint that servo controls. Figure INSERT displays the resulting joint angle as a function of the angle the servo is commanded to.

% 1034g

@@

The software is open-sourced Python based on the
code developed for the QuadraTot platform \citep{yosinski2011gaits}. All code is
available on the project website \citep{WEB}. We use an infrared light
emitting diode (LED) on the robot along with an external Nintendo Wii
remote to provide feedback of the distance traveled. The robot
receives feedback from the Wii remote and internal servo sensors and
then processes the information to send the next command to
the servos. The communication between the external control computer
and the ArbotiX on-board microcontroller occurs over wireless XBee.

@@

This work was supported by the National Science Foundation's Office of
Emerging Frontiers in Research and Innovation (grant number 0735953).

>>>>

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{fig5.jpg}
\caption{A rendered CAD model of Aracna. Note the lack of heavy servos on the legs themselves, which are instead controlled via four-bar linkages by servos in the robot's core.}
\label{cadModelOfRobot}
\end{center}
\end{figure}

@@

Initially, we eliminated the QuadraTot's fit-PC, an onboard Linux computer weighing 370g, and replaced it with an on-board ArbotiX microcontroller that weights only 47g. As a result, the main processing occurs on an external computer and commands are sent to Aracna wirelessly. This change, of course, comes of the cost of the robot being truly autonomous. Wireless communication between the external control computer
and the ArbotiX  microcontroller occurs over wireless XBee.

@@

A final change was to upgrade the power of the servo motors in order to increase the ability of the robot to strike whichever configurations are specified by the learning algorithms. Specifically, we upgraded from Dynamixel AX 12+ motors to AX-18A motors, which have a higher stall torque (1.8Nm vs. 1.5Nm at 12V), a higher stall current (2.2A vs 1.5A), and a higher no load speed (97 vs. 59 RPM).

@@

The body of Arcana takes advantage of 3D printing technology, also known as additive manufacturing, which generates physical objects from digital designs by building them up layer by layer~\citep{gibson2009additive, lipson2010factory}. The use of 3D printing means that other Aracna users can easily make copies of Aracna, either by having access to a 3D printer or via online 3D printing services such as Shapeways.com. Either option requires the 3D design files in the stereolithography (STL) format, which we are publishing in the online support material for this paper~\citep{WEB}. Moreover, to catalyze innovation in this open-source hardware project, we are also providing the source files for the SolidWorks computer-aided-design program, because it is easier to modify a design with the original source files than with STL files. It should thus be easy for future Aracna users to improve or alter the design and quickly obtain a physical instantiation of the design. Importantly, the use of 3D printing eliminates the need to know how to machine parts, allowing many more researchers to participate in using physical robot morphologies that they design themselves. These ideas are in line with a broader trend toward enabling non-technical users to design and manufacture physical objects~\citep{clune2011objects, clune2011endless, lipson2010factory}.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=.37\textwidth]{fig2.jpg}
\caption{A draft version of Aracna that was printed in one piece. This non-modular design proved expensive to maintain if part of the robot was damaged, and was replaced in a later version with a modular design. This image is of the printed body with support material still present.}
\label{notYetCleanedOnePieceRobot}
\end{center}
\end{figure}

@@

In addition to reducing the weight of the legs, the four-bar
mechanisms also satisfied the design goal of making a robot that had
non-traditional movements. Unusual kinematics make for a more effective evolutionary robotics test platform, since evolutionary algorithms are most helpful in domains that humans find hard to program solutions for. The reason Aracna's kinematics are counter-intuitive is because there is a complicated mapping between each servo's output and the movement of the joint controlled by that servo~(Figure~INSERTjointAnglesAsAFunctionOfServoPositions). INSERT-OTHER-REASONS-THE-KINEMATICS-ARE-STRANGE.

The range of motion for the hip joint is INSERT degrees and that of the knee joint is INSERT degrees~(Figure~INSERT). The range of the knee joint technically depends on the position of the hip joint, but the effect is slight enough (less than INSERT) degrees, that it can be effectively ignored.

There are two different ways to encode movements for Aracna, increasing its flexibility as a testing platform. The first method is to specify a sequence of positions over time for all eight servos. In this method the joint angles would be determined as shown in Figure~INSERTjointAnglesAsAFunctionOfServoPositions). The second method is to set the speed of each servo (and possibly its initial position). This method is possible because with the four bar mechanism a servo constantly rotating in one direction will move the joint back and forth between its minimum and maximum opening angle. This latter method provides a much smaller search space and would encourage regular gaits, which have been shown to be beneficial when evolving gaits for legged robots~\citep{clune2011performance, hornby2005autonomous}.

@@

The software, which is also open-source and freely available~\citep{WEB}, is written in Python and based on the
code developed for the QuadraTot platform~\citep{yosinski2011gaits}. The software translates a series of requested joint angles from the learning algorithm into servo movements. Additionally, it returns information to the learning algorithm, such as the distance traveled or the specific trajectory the robot took, so the learning algorithm can assess the quality of the gait. To provide this information, an infrared light
emitting diode (LED) was placed on the robot and a Nintendo Wii
remote was attached overhead. The software uses the combination of the two to ascertain the X, Y position of the robot. The software is interoperable with any gait or behavior learning algorithm.

\section{Example Gaits}

Evolutionary algorithms work best when they have a gradient to follow, instead of searching for a needle in a haystack. To get a sense of how randomly-generated gaits would perform, we randomly chose a few parameters....INSERT DESCRIPTION OF WHAT YOU DID, HOW IT WORKED, AND A LINK TO THE VIDEO.

\section{Conclusion}

I think we should wait until the rest of the paper is fleshed out before writing this.

@@

This work was supported by the National Science Foundation's Office of
Emerging Frontiers in Research and Innovation (grant number 0735953) and an NSF Postdoctoral Research Fellowship in Biology to Jeff Clune (DBI-1003220).
